Incremental λ-Calculus in Cache-Transfer Style

### 2017-07-11 popl18/source-language.tex
Fix typo
Style

If $\iectxlookup\iectx\tdf$ is a replacement,
$\rulename{SDReplaceCall}$ applies. Replacing the value of~$\tf$
in the environment forces the recomputation of~$\tf\,\tx$ from
scratch in the new environment. The resulting value~$\sclosedvalue'_\ty$
is the new value which must replace~$\sclosedvalue_\ty$: therefore
$\tdy$ equals~$\replace{\sclosedvalue'_\ty}$ in that case.

If $\iectxlookup\iectx\tdf$ is a nil change. We have two rules
depending on the nature of $\iectxlookup\iectx\tf$. If
$\iectxlookup\iectx\tf$ is a closure, $\rulename{SDClosureNil}$
applies and in that case the nil change of~$\iectxlookup\iectx\tf$ is
the exact same closure. Hence, to compute $\tdy$, we must reevaluate
this closure applied to the updated
argument~$\iectxlookup{\newenv\iectx}\tx$ to a
value~$\sclosedvalue'_\ty$ and bind~$\tdy$ to
$\replace{\sclosedvalue'_\ty}$. In other words, this rule is
equivalent to $\rulename{SDReplaceCall}$ in the case where a closure
is replaced by itself.%
\begin{poplForThesis}
\footnote{Based on \cref{ch:bsos}, we are confident we
could in fact use the derivative of $\sterm_f$;}
\end{poplForThesis}
%
If $\iectxlookup\iectx\tf$ is a primitive, $\rulename{SDPrimitiveNil}$
applies. The nil change of a primitive~$\sprim$ is its derivative
which interpretation is realized by a
function~$\Delta_\sprim(\param)$.  The evaluation of this function on
the input value and the input change leads to the
change~$\icloseddvalue_\ty$ bound to $\tdy$.

>>>>

If $\iectxlookup\iectx\tdf$ is a replacement,
$\rulename{SDReplaceCall}$ applies. Replacing the value of~$\tf$
in the environment forces recomputing~$\tf\,\tx$ from
scratch in the new environment. The resulting value~$\sclosedvalue'_\ty$
is the new value which must replace~$\sclosedvalue_\ty$, so
$\tdy$ binds to~$\replace{\sclosedvalue'_\ty}$ when evaluating the
$\textbf{let}$ body.

If $\iectxlookup\iectx\tdf$ is a nil change, we have two rules
depending on the nature of $\iectxlookup\iectx\tf$. If
$\iectxlookup\iectx\tf$ is a closure, $\rulename{SDClosureNil}$
applies and in that case the nil change of~$\iectxlookup\iectx\tf$ is
the exact same closure. Hence, to compute $\tdy$, we must reevaluate
this closure applied to the updated
argument~$\iectxlookup{\newenv\iectx}\tx$ to a
value~$\sclosedvalue'_\ty$ and bind~$\tdy$ to
$\replace{\sclosedvalue'_\ty}$. In other words, this rule is
equivalent to $\rulename{SDReplaceCall}$ in the case where a closure
is replaced by itself.%
\begin{poplForThesis}
\footnote{Based on \cref{ch:bsos}, we are confident we
could in fact use the derivative of $\sterm_f$;}
\end{poplForThesis}
%
If $\iectxlookup\iectx\tf$ is a primitive, $\rulename{SDPrimitiveNil}$
applies. The nil change of a primitive~$\sprim$ is its derivative
which interpretation is realized by a
function~$\Delta_\sprim(\param)$.  The evaluation of this function on
the input value and the input change leads to the
change~$\icloseddvalue_\ty$ bound to $\tdy$.
